Project Proposal

### 2024-11-15 CURJ_IDS702Projectproposal.qmd
County data initial load & transform

```{r data-1, warning=FALSE}
texas_full <- read.csv('https://github.com/rrandev03/Practical-Data-Science/raw/refs/heads/main/Texas.csv', skip=1)
#colnames(texas_full)
```

```{r}
texas <- texas_full[c('FIPS', 'State', 'County', "Segregation.Index", "Spending.per.Pupil", "School.Funding.Adequacy", "Segregation.Index.1", "Juvenile.Arrest.Rate")]
head(texas)
```
```{r}
texas <- texas |> 
  rename(
    Residential.Segregation.Index = Segregation.Index.1)

head(texas)
```

>>>>

```{r data-1, warning=FALSE}
alabama_full <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/county_data/Alabama.csv', skip=1)
texas_full <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/county_data/Texas.csv', skip=1)
nc_full <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/county_data/North%20Carolina.csv', skip=1)
colorado_full <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/county_data/Colorado.csv', skip=1)
washington_full <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/county_data/Washington.csv', skip=1)
ny_full <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/county_data/New%20York.csv', skip=1)
minnesota_full <-  read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/county_data/Minnesota.csv', skip=1)
#colnames(texas_full)
```

```{r}
head(alabama_full)
```

```{r}
desired_cols <- c('FIPS', 'State', 'County', "Segregation.Index", "Spending.per.Pupil", "School.Funding.Adequacy", "Segregation.Index.1", "Juvenile.Arrest.Rate")

alabama <- alabama_full[desired_cols]
texas <- texas_full[desired_cols]
nc <- nc_full[desired_cols]
ny <- ny_full[desired_cols]
washington <- washington_full[desired_cols]
colorado <- colorado_full[desired_cols]
minnesota <- minnesota_full[desired_cols]

```{r}
texas <- texas |> 
  rename(
    School.Segregation.Index = Segregation.Index,
    Residential.Segregation.Index = Segregation.Index.1)

alabama <- alabama |> 
  rename(
    School.Segregation.Index = Segregation.Index,
    Residential.Segregation.Index = Segregation.Index.1)

nc <- nc |> 
  rename(
    School.Segregation.Index = Segregation.Index,
    Residential.Segregation.Index = Segregation.Index.1)

ny <- ny |> 
  rename(
    School.Segregation.Index = Segregation.Index,
    Residential.Segregation.Index = Segregation.Index.1)

washington <- washington |> 
  rename(
    School.Segregation.Index = Segregation.Index,
    Residential.Segregation.Index = Segregation.Index.1)

colorado <- colorado |> 
  rename(
    School.Segregation.Index = Segregation.Index,
    Residential.Segregation.Index = Segregation.Index.1)

minnesota <- minnesota |> 
  rename(
    School.Segregation.Index = Segregation.Index,
    Residential.Segregation.Index = Segregation.Index.1)

head(minnesota)
```

```{r}
all_states <- rbind(alabama, texas, nc, ny, washington, colorado, minnesota)
all_states[sample(nrow(all_states), 10), ]
```

```{r}
all_states_final <- all_states |>
  mutate(Region = factor(case_when(
    State == 'Texas' ~ 'West South Central', # use NA to set a value to missing
    State == 'Alabama' ~ 'East South Central',
    State == 'North Carolina' ~ 'South Atlantic',
    State == 'New York' ~ 'Middle Atlantic',
    State == 'Washington' ~ 'Pacific',
    State == 'Colorado' ~ 'Mountain',
    State == 'Minnesota' ~ 'West North Central',
    TRUE ~ State #this says to keep all other values the same
  )), School.Funding.Cat = factor(case_when(
    School.Funding.Adequacy < 0 ~ 'Inadequate', # use NA to set a value to missing
    School.Funding.Adequacy > 0  ~ 'Adequate',
  TRUE ~ NA
  )))

all_states_final[sample(nrow(all_states_final), 10), c('State', 'County', 'School.Funding.Adequacy', 'Region', 'School.Funding.Cat')]
```
```{r}
